A preliminary constraint grammar for Russian

### 2015-02-19 2015-nodalida-ruscg/ruscg.tex
organise
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59019 72bbbca6-d526-0410-a7d9-f06f51895060
average is better
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59020 72bbbca6-d526-0410-a7d9-f06f51895060
more stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59021 72bbbca6-d526-0410-a7d9-f06f51895060

@@

\section{Review of literature}
% ROB + FRAN
% different CGs 
% faroese
% estonian
%

@@

\begin{table*}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    \textbf{Domain} & \textbf{Tokens} & \textbf{Precision} & \textbf{Recall} & \textbf{Ambig. solved} \\
    \hline
    Wikipedia       & 7,857      & 0.506        & 0.996    & 44.92\%  \\
    News            & 642        & 0.471        & 0.990    & 41.60\%  \\
    Literature      & 1,652      & 0.473        & 0.984    & 42.95\%  \\
    \hline
    Total           & 10,150     & 0.498        &  0.994   &  44.39\% \\
    \hline
  \end{tabular}
  \caption{Results for the test corpora.}
\end{table*}

>>>>

Our purposes: Processing stressed wordforms and open-source machine translation

@@

\section{Review of literature}
% ROB + FRAN
% different CGs 
% faroese
% estonian

State-of-the-art morphological analysis in Russian is primarily based on finite-
state technology \cite{Nozhov-03,Segalovich-03}, although some success has 
also been found with machine-learning approaches \cite{sharoff08lrec-mocky}. 
However, no existing Russian morphology tools were suitable for our needs, so
we have 
The resources described in this paper Therefore, we developed free and 
open-source finite-state 
tools capable of analyzing and generating stressed wordforms, based on the
well-known \emph{Grammatical Dictionary of Russian} \cite{Zaliznjak-77}.
Our Finite-State Transducer\footnote{Using two-level 
morphology \cite{Koskenniemi-84}, implemented in both xfst
\cite{Beesley.Karttunen-03} and hfst \cite{hfst-11}} (FST) generates all possible 
morphosyntactic readings of each wordform, and our Constraint 
Grammar\footnote{Implemented using vislcg3 constraint grammar parser
(http://beta.visl.sdu.dk/cg3.html).}
\cite{Karlsson-90,Karlsson.Voutilainen.ea-95} then removes
some readings based on syntactic context.

@@

\begin{table*}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    \textbf{Domain} & \textbf{Tokens} & \textbf{Precision} & \textbf{Recall} & \textbf{Ambig. solved} \\
    \hline
    Wikipedia       & 7,857      & 0.506        & 0.996    & 44.92\%  \\
    Literature      & 1,652      & 0.473        & 0.984    & 42.95\%  \\
    News            & 642        & 0.471        & 0.990    & 41.60\%  \\
    \hline
    \textbf{Average}& 10,150     & 0.498        &  0.994   &  44.39\% \\
    \hline
  \end{tabular}
  \caption{Results for the test corpora.}
\end{table*}
